NumPy---Array Computation for Python

### 2019-12-20 paper.tex
Add acknowledgments and contributions

@@

%Must include all authors, identified by initials, for example: A.A.
%conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A.
%and D.A. analysed the results.  All authors reviewed the manuscript.

>>>>

S.J.v.d.W and K.J.M. were funded in part by the Gordon and Betty Moore
Foundation through Grant GBMF3834 and by the Alfred P. Sloan Foundation through
Grant 2013-10-27 to the University of California, Berkeley.
S.B., T.J.R., and W.W. were funded in part by the Gordon and Betty Moore 
Foundation through Grant GBMF5447 and by the Alfred P. Sloan Foundation through
Grant G-2017-9960 to the University of California, Berkeley.

@@

%C.R.H and T.E.O.
S.J.v.d.W and K.J.M. composed the manuscript with input from others.
All authors have contributed significant code, documentation, and/or expertise
to the NumPy project.
All authors reviewed the manuscript.
